TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
Sec 5

\section{Feature Extraction}\label{sec:features}
We explain the construction of the similarity measure by which relevant
objects are predicted

@@

Here are the different kind of feature we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single placeholder $V$,
\item names of the variables.
\end{itemize}
Goals (respectively theorems) are represented by a couple of a list of
terms (assumptions) and a term (conclusion). So, we distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The union of all those
features are considered the feature of a goal (respectively theorem). From
that, we can construct features for a list of goals by
from the union of the features of each goal in the list.

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally modify the weight by raising them to the sixth power giving
even more credence
to rare features. This modification was found experimentally optimal in
\cite{ckju-pxtp13}.

The first co-distance $sim_1$ sums the weight of each shared
features to compute the total score.
In a second co-distance $sim_2$, we additionally take
the total number of features into account, to reduce the seemingly unfair
advantage of big
feature sets in the first scoring function.
\[sim_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_0 \cap
<f_1}{\text{tfidf}(f)^{6}}}\]
\[sim_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_0 \cap
f_1}{\text{tfidf}(f)^{6}}}}
{ln (e + \mathit{card} f_0 + \mathit{card} f_1)}\]

@@

The first idea is to select tactic-goal pairs and theorems by their similarity
with $c$ (i.e. $\mathit{Predictions}^{\mathit{tactic}}_{500} (c)$ and
$\mathit{Predictions}^{\mathit{theorem}}_{500} (c)$).
However, this selection may not be adapted to later stages of
the proof where goals may have drifted significantly from $c$. In order to
anticipate the production of diverse goals, our prediction during preselection
takes dependencies between objects of the same dataset into account.
This dependency relation is assymetric. Through the relation, each object has
multiple children and at most one parent.
Once a dependency relation is established we can calculate a dependency score
for each object, which is the maximum of its similarity score
and the similarity score of its parent. In the end, the 500 entries with
highest dependency score are preselected in each dataset.

@@

\begin{definition}(Dependencies of a tactic-goal pair)\\
Let $\mathfrak{F}$ be the set of recorded tactic-goal pairs.
The dependencies $D_\infty$ of a tactic-goal pair $(t_0,g_0)$ is
inductively defined by:

@@

To preselect a list of goal $l$ from our database of lists of goals, we
consider the tactic input $g$ that was at the origin of the production of $l$
during orthogonalization. The list $l$
is preselected if and only if $g$ appears in the 500 preselected tactic-goal
pairs. This has the
desirable effect that negative and positive examples derived from the same
input goal are chosen or discarded together.
\todo{this paragraph was confusing for Lasse}

>>>>

\section{Feature Extraction}\label{sec:features}
\todo{@TG: decide which of the next sentences}
We explain the construction of the similarity measure by which relevant
objects are predicted

@@

Here are the different kinds of feature we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single placeholder $V$,
\item names of the variables.
\end{itemize}
Goals (respectively theorems) are represented by pairs consisting of a list of
terms (assumptions) and a term (conclusion). We distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The feature of a goal (respectively theorem)
are the union of all these tagged features. From
that, we can construct features for a list of goals by computing the union of the features of each goal in the list.

\subsection{Similarity}\label{sec:predictions}
We estimate the similarity (or co-distance) between two objects $o_1$ and $o_2$
through their respective feature sets $f_1$ and $f_2$.
The estimation is based on the frequency of the features in the intersection of
$f_1$ and $f_2$. A good rule of thumb is that the rarer the shared features
are, the more similar two goals should be. The relative rarity of each feature
can be estimated by calculating its TF-IDF weight~\cite{Jones72astatistical}.
We additionally raise these weighs to the sixth power giving
even more importance
to rare features. This modification was found experimentally optimal in
\cite{ckju-pxtp13}.

The first co-distance $sim_1$ sums the weight of all shared
features to compute the total score.
In a second co-distance $sim_2$, we additionally take
the total number of features into account, to reduce the seemingly unfair
advantage of big
feature sets in the first scoring function.
\[sim_1 (o_1, o_2) = {\sum\nolimits_{\,f \in f_0 \cap
<f_1}{\text{tfidf}(f)^{6}}}\]
\[sim_2 (o_1, o_2) = \frac{{\sum\nolimits_{\,f \in f_0 \cap
f_1}{\text{tfidf}(f)^{6}}}}
{ln (e + \mathit{card} f_0 + \mathit{card} f_1)}\]

@@

The first idea is to select tactic-goal pairs and theorems by their similarity
with $c$ (i.e. $\mathit{Predictions}^{\mathit{tactic}}_{500} (c)$ and
$\mathit{Predictions}^{\mathit{theorem}}_{500} (c)$).
However, this selection may not be adapted at later stages of
the proof where goals may have drifted significantly from $c$. In order to
anticipate the production of diverse goals, our prediction during preselection
takes dependencies between objects of the same dataset into account.
This dependency relation is asymmetric. Through the relation, each object has
multiple children and at most one parent.
Once a dependency relation is established we can calculate a dependency score
for each object, which is the maximum of its similarity score
and the similarity score of its parent. Finally, the 500 entries with
highest dependency score are preselected in each dataset.

@@

\begin{definition}(Dependencies of a tactic-goal pair)\\
Let $\mathfrak{F}$ be the set of recorded tactic-goal pairs.
The dependencies $D_\infty$ of a tactic-goal pair $(t_0,g_0)$ are
inductively defined by:

@@

To preselect a list of goal $l$ from our database of lists of goals, we
consider the tactic input $g$ that was at the origin of the production of $l$
during orthogonalization. The list $l$
is preselected if and only if $g$ appears in the 500 preselected tactic-goal
pairs. This has the
desirable effect that negative and positive examples derived from the same
input goal are chosen or discarded together.
\todo{this paragraph was confusing for Lasse and Cezary}
